Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spread Across 400\,pc

### 2021-03-10 cluster_paper/ms.tex
update ms

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.75\textwidth]{f5a.pdf}
		}

		\subfloat{
			\includegraphics[width=0.75\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Lithium equivalent widths in NGC\,2516,}
  plotted against extinction-corrected color ({\it top}), and the
  combination of rotation period and extinction-corrected color ({\it
  bottom}).
  {\bf TODO: Do this against the autorot sample; Add the GALAH EWs}
  \label{fig:lithium}
  }
\end{figure*}

The third and final approach we took for confirming the youth of the
halo population of \cn\ was an analysis of the Li\,\textsc{I}
6708\,\AA doublet.  The method is reviewed by
\citet{soderblom_ages_2010}, and its connection to stellar rotation
has recently been surveyed by \citet{bouvier_lithium-rotation_2020}.
For \cn, two spectroscopic datasets  seemed particularly important:
Gaia-ESO \citep{randich_gaiaeso_2018} and GALAH DR3
\citep{buder_galah_2020}.  The target selection and results from each
survey were as follows.

Gaia-ESO selected {\it cluster candidates} to be observed with the
GIRAFFE and UVES spectrographs based on previously reported literature
members and publicly available optical and NIR photometry.  This
target selection approach included some stars in the spatial proximity
of previously known members.  Since the existence of the \cn\ halo was
not known at the time of targetting, very few ``halo'' stars are in
their sample.  For \cn, \citet{randich_gaiaeso_2018} ultimately
reported stellar parameters (including lithium equivalent widths and
metallicities) for 796 stars that they considered possible \cn\
members.  Cross-matching against our kinematic list of \nkinematic
candidate members by position and imposing a 0$\farcs$5 maximum
separation limit yields 492 kinematic members for which a Gaia-ESO
spectrum was acquired and stellar parameters were reported.  15 of
these (all with $(Bp-Rp)_0 > 2.0$) are spurious matches based on the
Gaia color and GES effective temperature, and we remove them.  This
yields 477 stars, of which 436 are in the core, and 41 are in the
halo.  The lop-sided ratio is primarily caused by the Gaia-ESO
selection function.

@@

\section{Kinematics $\otimes$ Rotation}

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		%\subfloat{
			\includegraphics[width=0.49\textwidth]{f5a.pdf}
		%	\includegraphics[width=0.59\textwidth]{f5b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Lithium in the core and halo of NGC\,2516.}
  Equivalent width of the 6708\,\AA\ doublet is shown
  versus extinction-corrected color for all kinematic \cn\ members
  with Gaia-ESO ($N=452$) or GALAH ($N=107$) spectra available.
  The GALAH spectra comprise slightly over half of the halo stars,
  due to the non-targeted selection function of that survey.
  Points with ${\rm EW}\approx0\,$m\AA\ are non-detections.
  \label{fig:lithiumcorehalo}
  }
\end{figure}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		%\subfloat{
		\includegraphics[width=1\textwidth]{f5b.pdf}
		%	\includegraphics[width=0.59\textwidth]{f5b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Lithium and rotation in NGC\,2516.}
		Points show all kinematic \cn\ members with TESS rotation
		periods in the Gaia-ESO or GALAH surveys, and are colored by
		equivalent width.
	   Non-detections appear with ${\rm EW}\approx0\,$m\AA.
	The K-dwarfs shows a similar lithium-rotation correlation
		to what has been previously observed,
		and is discussed in Section~\ref{subsec:lithium}.
		\label{fig:lithium}
	}
\end{figure*}

The third and final approach we took for confirming the youth of the
halo population of \cn\ was an analysis of the Li\,\textsc{I}
6708\,\AA\ doublet.  The method has been reviewed by
\citet{soderblom_ages_2010}, and its connection to stellar rotation
has recently been surveyed by \citet{bouvier_lithium-rotation_2020}.
For \cn, two spectroscopic datasets  seemed particularly important:
Gaia-ESO \citep{randich_gaiaeso_2018} and GALAH DR3
\citep{buder_galah_2020}.  The target selection and results from each
survey were as follows.

Gaia-ESO selected {\it cluster candidates} to be observed with the
GIRAFFE and UVES spectrographs based on previously reported literature
members and publicly available optical and NIR photometry.  This
target selection approach included some stars in the spatial proximity
of previously known members.  Since the existence of the \cn\ halo was
not known at the time of target selection, very few ``halo'' stars are in
the sample.  For \cn, \citet{randich_gaiaeso_2018} ultimately
reported stellar parameters (including lithium equivalent widths and
metallicities) for 796 stars that they considered possible \cn\
members.  Cross-matching against our kinematic list of \nkinematic
candidate members by position and imposing a 0$\farcs$5 maximum
separation limit yields 492 kinematic members for which a Gaia-ESO
spectrum was acquired and stellar parameters were reported.  15 of
these (all with $(Bp-Rp)_0 > 2.0$) are spurious matches based on the
Gaia color and GES effective temperature, and we remove them.  This
yields 477 stars, of which 436 are in the core, and 41 are in the
halo.  The lop-sided ratio is primarily caused by the Gaia-ESO
selection function.
%FIXME VERIFY THAT THESE NUMBERS DON'T INCLUDE THEIR NANS...

@@

\section{Kinematics $\otimes$ Rotation}
\label{app:gaia6d_x_rotn}
